\documentclass[letterpaper]{article}
\usepackage[submission]{aaai2027}
\usepackage[hyphens]{url}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algorithmic}
\urlstyle{rm}
\def\UrlFont{\rm}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/TemplateVersion (2027.1)
}

\setcounter{secnumdepth}{0}

\title{Safety Is a Claim, Not a Cost: Calibrated Action Certificates for Offline RL under Moving Constraints}

\author{
    Anonymous Submission
}
\affiliations{
    Paper ID withheld for double-blind review.
}

\begin{document}

\maketitle

\begin{abstract}
Offline safe reinforcement learning is usually evaluated by aggregate reward and cost under one or a few constraint budgets.
This is an incomplete form of deployment evidence: a policy can satisfy an aggregate episode budget while relying on actions whose safety claims are unsupported under the requested deployment constraint.
We study this deployability gap and propose action-conditional conformal certificates (ACCS), a post-hoc protocol that turns candidate policy actions into calibrated action-level safety claims with explicit provenance.
ACCS builds a budget-uniform upper-cost certificate surface, executes or replaces actions whose claims are supported, and abstains when calibration evidence is insufficient.
The intended contribution is not another constraint-adaptive policy optimizer, but a deployment evidence layer that can wrap offline safe RL methods, including strong policy-switching competitors.
\end{abstract}

\section{Introduction}

The current draft route is maintained in \texttt{../idea\_blueprint.md}.
This file is a format-valid AAAI-27 skeleton only; paper-facing claims must not be added before the Phase 0 literature gate and Phase 1 deployability-gap toy phenomenon are recorded.

\section{Problem Setup}

We consider an offline dataset collected under a behavior policy, a learned base policy, and deployment requests specified by cost budgets or safety constraints that may differ from those used during training or model selection.

\section{Method}

ACCS will be described as a budget-uniform claim-issuing protocol:

\begin{enumerate}
    \item fit nonconformity scores for candidate actions on a held-out calibration split;
    \item condition calibration by action groups, budget ranges, or risk clusters;
    \item execute, replace, or abstain according to the calibrated action-safety claim;
    \item report certified utility, claim yield, claim miscoverage, unsupported safety success, budget adaptivity, and horizon-level audit metrics.
\end{enumerate}

\section{Experiments}

The first experiment must establish a clean deployability-gap failure mode before broad benchmark runs.
Direct competitors and reusable benchmark code are tracked in \texttt{../papers/literature\_review.md}.

\section{Conclusion}

Placeholder.

\bibliography{references}

\end{document}
